---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# Setup

```{r}
library(neo4jshell)

my_con <- 
    list(
        address = "neo4j://localhost:7687",
        uid = "",
        pwd = ""
    )

neo4j_query(
    con = my_con,
    qry = 
    "CALL apoc.stats.degrees('>');"
)

```


```{r}
library(targets)
```

```{targets globals, tar_globals = TRUE}

options(tidyverse.quiet = TRUE)

tar_option_set(
  packages = c(
    "dplyr", "readr",
    "ggraph", "tidygraph"
  )
)
```

# Targets

```{targets raw_files}
list(
  tar_target(
    nodes_raw_file,
    "O:\\Preventive Medicine\\Keiki-DanRiggins\\CountyCare Opioid Analgesic Prescriber\\p_attr_core.csv",
    format = "file"
  ),
  tar_target(
    edges_raw_file,
    "O:\\Preventive Medicine\\Keiki-DanRiggins\\CountyCare Opioid Analgesic Prescriber\\Providers_Edgelist.csv",
    format = "file"
  )
)
```

```{targets raw_imports}
list(
  tar_target(
    nodes_raw,
    read_csv(nodes_raw_file) |> 
      mutate(ID = as.character(ID))
  ),
  tar_target(
    edges_raw,
    read_csv(edges_raw_file) |> 
      rename(from = SOURCE, to = TARGET)
  )
)
```

```{targets provider_graph, tar_simple = TRUE}
tbl_graph(
  nodes = nodes_raw,
  edges = edges_raw,
  directed = TRUE,
  node_key = "ID"
)
```




```{targets fit, tar_simple = TRUE}
biglm(Ozone ~ Wind + Temp, data)
```

# Pipeline

If you ran all the `{targets}` chunks in non-interactive mode, then your R scripts are set up to run the pipeline.

```{r}
tar_make()
```

# Output

You can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.

```{r, message = FALSE}
library(biglm)
tar_read(fit)
```

```{r}
tar_read(hist)
```

The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.
